Better JavaScript Runtime Understanding by Automated Function Name Extraction

### 2011-01-24 trunk/papers/issta2011/sigproc-sp.tex

\begin{table}
\centering
\caption{The total number of functions and the number of named functions in five famous JavaScript projects.}
  \begin{tabular}{ | l | l | c | c | c |}
  \hline
   Project & Description & Total & Named \\ 
  \hline 
   jQuery & JavaScript Library & 422 & 23 \\ 
  \hline 
   Prototype & JavaScript Framework & 645 & 203 \\ 
  \hline 
   Closure & Google Web Library & 9195 & 208 \\ 
  \hline 
   YUI &  Yahoo UI Library & 22346 & 922 \\ 
  \hline 
   Firebug & Web Development Tool & 3424 & 406 \\ 
  \hline 
  \end{tabular}
 \label{functions} 
\end{table}

@@

  \end{tabular}
  }
\end{table}

%to remove
To illustrate the second issue, we pause the program (Figure~\ref{js-code}) at line 15 by a breakpoint. Figure~\ref{debuggers-callstack} shows how the program callstack is displayed in Google Chrome debuggers and Firebug. The differences in the number of frames and line numbers between two callstacks are due to dissimilar event handling implementations in the underlying platforms. Google chrome shows {\small\texttt{anonymouse}} as the name of all functions excepting the first one. Firebug performs better by guessing three function names but it still fails in one case. In these cases, the information provided by debugger is useless and the developer has to locate the function source to understand or recall the function behaviour.

To illustrate the second issue, we pause the program (Figure~\ref{js-code}) at line 15 by a breakpoint. Figure~\ref{debuggers-callstack} shows how the program callstack is displayed in Google Chrome debuggers and Firebug. The differences in the number of frames and line numbers between two callstacks are due to dissimilar event handling implementations in the underlying platforms. Google chrome shows {\small\texttt{anonymouse}} as the name of all functions excepting the first one. Firebug performs better by guessing three function names but it still fails in one case. In these cases, the information provided by debugger is useless and the developer has to locate the function source to understand or recall the function behaviour.

To illustrate the second issue, we pause the program (Figure~\ref{js-code}) at line 15 by a breakpoint. Figure~\ref{debuggers-callstack} shows how the program callstack is displayed in Google Chrome debuggers and Firebug. The differences in the number of frames and line numbers between two callstacks are due to dissimilar event handling implementations in the underlying platforms. Google chrome shows {\small\texttt{anonymouse}} as the name of all functions excepting the first one. Firebug performs better by guessing three function names but it still fails in one case. In these cases, the information provided by debugger is useless and the developer has to locate the function source to understand or recall the function behaviour.

>>>>

\begin{table}
\centering
\caption{The total number of functions and the number of named functions in five famous JavaScript projects.}
  \begin{tabular}{ | l | l | c | c | c |}
  \hline
   Project & Description & Total & Named \\ 
  \hline 
   jQuery & JavaScript Library & 422 & 23 \\ 
  \hline 
   Prototype & JavaScript Framework & 645 & 203 \\ 
  \hline 
   Closure & Google Web Library & 9195 & 208 \\ 
  \hline 
   YUI &  Yahoo UI Library & 21080 & 901 \\ 
  \hline 
   Firebug & Web Development Tool & 3424 & 406 \\ 
  \hline 
  \end{tabular}
 \label{functions} 
\end{table}

@@

  \end{tabular}
  }
 \label{function-types} 
\end{table}

Table~\ref{function-types} shows JavaScript code corresponding to each case. The first one usually apears when developers try to group a set of functions in a new object. A common case is the {\small\texttt{prototype}} property of a constructor. It resembles the class structure in traditional object-oriented languages. When a new object is created by the constructor, the new object also inherits all functions defined in the constructor's prototype. Another case is when the owner object is a shared object which contains a set of utility functions. We assign the property name which the function body is assigned to as the function name.

In the second case, we first need to name the array literal contains the function body. If the name is {\small\texttt{foo}}, knowing the index of function body ({\small\texttt{i}}, {{\small\texttt{foo[i]}} is assigned as the function body name. The array literal can be consumed in a similar way as a function object (excepting the ninth case, as it can not be called), so the naming of array literal can be recursively done similar to a function object.

For the third and fourth cases where the function object is assigned to an object property we use the object property as the function name. In the fifth and sixth cases, {\small\texttt{bar}} can be an object or an array. For these two cases we use the expression inside {\small\texttt{[]}} as the function name. For the cases seven and eight, we use the left side of the assignment as the name candidate.

Calling functions objects just after their creations is a common pattern in JavaScript. This pattern is usually used for building modules employing the clousure feature in JavaScript. Although the function object usage is only limited to this call, functions inside the closure function(The function is being called) has access to the properties in the closure scope in the future calls.

\begin{table*}
\centering
\caption{The number nameless functions in each category defined in table~\ref{function-types}.}
  \begin{tabular}{ | l | c | c | c | c | c | c | c | c | c | c | c |}
  \hline
     & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 \\ 
  \hline 
   jQuery & 223(58\%) & 0  & 34(8\%) & 0 & 10(2\%) & 2 & 0 & 24(6\%) & 9(2\%) & 0 & 86(21\%)  \\ 
  \hline 
   Prototype & 265(60\%) & 0 & 28(6\%)& 0 & 0 & 1& 0 & 25(5\%)& 44(10\%)& 8(1\%) & 71(16\%) \\ 
  \hline 
   Closure & 23 (0.2\%)& 0 & 8465(94\%)& 3 & 4 & 0 & 0 & 67(0.7\%)& 16(0.2\%)& 43(0.5\%)& 365(4\%)\\ 
  \hline 
   YUI & 13278(66\%)& 6 & 1705(8\%)& 0 & 90(0.5\%)& 0 & 0 & 1121(6\%)& 171(1\%)& 93(0.5\%)& 3715(18\%)\\ 
  \hline 
   Firebug & 2296(76\%)& 0 & 539(18\%)& 1 & 0 & 0 & 0 & 14(0.5\%)& 7(0.2\%)& 6(0.2\%)& 149(5\%) \\ 
  \hline 
   Total & 49\%& 0\% & 33\% & 0\% & 0.3\% & 0\% & 0\% & 4\%& 0.7\%& 0.5\%& 13\% \\ 
  \hline 
  \end{tabular}
 \label{functions-types-count} 
\end{table*}
